Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-24 Docs/TODAES/paper.tex
minor changes
minor changes to use ACM pattern for algorithm

\documentclass[prodmode,acmtrets]{acmsmall} % Aptara syntax

@@

\vspace{3 mm}
\begin{lstlisting}[language=C,caption={OpenMP basic Example.},label={lst:example},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{lstlisting}

\vspace{1.5 mm}
In the above example, the {\it for} loop is executed in parallel. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor. There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\textit{\#pragma omp critical}'' directive is routinely used.

@@

\vspace{3 mm}
\begin{lstlisting}[language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
(Declare-Const K Int) 
(Declare-Const W Int)
(assert (< K 2)) 
(assert (< (- W K) 1))
(maximize (+ K W)) 
(check-sat)
\end{lstlisting}

\vspace{1.5 mm}
Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.

@@

Based on~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $. The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
%
\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{V_i \in V_h} h_i,
\end{align}
%
\vspace{2 mm}
\noindent and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
%
%
%  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
\begin{align}
\label{software-communication-costs}
  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j).
\end{align}

@@

\vspace{1.5 mm}
\begin{lstlisting}[caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
Initialize variables 
Declare number of nodes and edges
Declare hardware cost of each node as array (h)
Declare software cost of each node as array (s)
Declare communication cost of each edge (c)
Declare the initial software cost of ($S_0$)
Declare transposed incidence matrix graph G (E)
Define the solutions variable ($X_i$) as Boolean
main {
  For TipH = 0 to Hmax Do {
    Populate $X_i$ with nondeterministic / test values
    Calculate s(1-x)+c|Ex| and store at variable
    Requirement isued by Assume (Variable <= $S_0$)
    Calculate Hp cost Based on value tested of $X_i$
    Violation check with Assert(Hp > TipH)
  }
}
\end{lstlisting}

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
%  GetNextStep(){
%  int largestChunk = -1;
%  chunk largest;
%  for each(chunk in chunks){
%     if(chunk.right - chunk.left > largestChunk){
%           largestChunk = chunk.right - chunk.left;
%           largest = chunk;
%     }
%   }	
%   chunks.remove(largest);	
%   int median = largest.left + floor((largest.right - largest.left) / 2)
%   if(median > 0){
%      if(largest.right - largest.left > 1)
%         chunks.add(new chunk(largest.left, median - 1));	
%      if(largest.right != largest.left)
%         chunks.add(new chunk(median + 1, largest.right);
%    }
%   return median;
% }
%\end{minted}
%\caption{Steps calculation using intervals.}
%\label{Steps-Calculation-using-Intervals}
%\end{listing}
\vspace {2 mm}
\begin{lstlisting}[caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
    if(chunk.right - chunk.left > largestChunk){
      largestChunk = chunk.right - chunk.left;
      largest = chunk;
    }
  }	
  chunks.remove(largest);	
  int median = largest.left + floor((largest.right-largest.left)/2)
  if(median > 0){
    if(largest.right - largest.left > 1)
      chunks.add(new chunk(largest.left, median - 1));	
    if(largest.right != largest.left)
      chunks.add(new chunk(median + 1, largest.right);
  }
  return median;
}
\end{lstlisting}

@@

\vspace {2 mm}
\begin{lstlisting}[caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
--Initialize Variables
  Create vZ context 
  Create binary vector (x)
  Declare number of nodes, edges and $S_0$
  Declare hardware cost of each node as array (h) 
  Declare software cost of each node as array (s)
  Declare communication cost of each edge (c)
  Declare transposed incidence matrix graph G(E)
--Arithmetic Expressions
  SC = s(1-x)
  CMC = c*|EX|
  Fobj =  x[i] * h[i]
--Assert Constraints
  Add constraints (SF + CMC <= $S_0$)
  Add constraints to minimize Fobj
  Check Model
  Print Result
\end{lstlisting}

>>>>

\documentclass[prodmode,acmtodaes]{acmsmall} % Aptara syntax

@@

\vspace{2 mm}
\begin{lstlisting}[basicstyle=\small,language=C,caption={OpenMP basic Example.},label={lst:example},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{lstlisting}

In the above example, the {\it for} loop is executed in parallel. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor. There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\textit{\#pragma omp critical}'' directive is routinely used.

@@

\vspace{2 mm}
\begin{lstlisting}[basicstyle=\small,language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
(Declare-Const K Int) 
(Declare-Const W Int)
(assert (< K 2)) 
(assert (< (- W K) 1))
(maximize (+ K W)) 
(check-sat)
\end{lstlisting}

Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.

@@

Based on~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $. The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
%
\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{V_i \in V_h} h_i,
\end{align}

\vspace{2 mm}
\noindent
and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
%
%
%  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
\begin{align}
\label{software-communication-costs}
  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j).
\end{align}

@@

\vspace{2 mm}
\begin{lstlisting}[basicstyle=\small,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
Initialize variables 
Declare number of nodes and edges
Declare hardware cost of each node as array (h)
Declare software cost of each node as array (s)
Declare communication cost of each edge (c)
Declare the initial software cost of ($S_0$)
Declare transposed incidence matrix graph G(E)
Define the solutions variable ($X_i$) as Boolean
main {
  For TipH = 0 to Hmax Do {
    Populate $X_i$ with nondeterministic / test values
    Calculate s(1-x)+c|Ex| and store at variable
    Requirement isued by Assume (Variable <= $S_0$)
    Calculate Hp cost Based on value tested of $X_i$
    Violation check with Assert(Hp > TipH)
  }
}
\end{lstlisting}

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
%  GetNextStep(){
%  int largestChunk = -1;
%  chunk largest;
%  for each(chunk in chunks){
%     if(chunk.right - chunk.left > largestChunk){
%           largestChunk = chunk.right - chunk.left;
%           largest = chunk;
%     }
%   }	
%   chunks.remove(largest);	
%   int median = largest.left + floor((largest.right - largest.left) / 2)
%   if(median > 0){
%      if(largest.right - largest.left > 1)
%         chunks.add(new chunk(largest.left, median - 1));	
%      if(largest.right != largest.left)
%         chunks.add(new chunk(median + 1, largest.right);
%    }
%   return median;
% }
%\end{minted}
%\caption{Steps calculation using intervals.}
%\label{Steps-Calculation-using-Intervals}
%\end{listing}
\vspace {2 mm}
\begin{lstlisting}[basicstyle=\small,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
    if(chunk.right - chunk.left > largestChunk){
      largestChunk = chunk.right - chunk.left;
      largest = chunk;
    }
  }	
  chunks.remove(largest);	
  int median = largest.left + floor((largest.right - largest.left) / 2)
  if(median > 0){
    if(largest.right - largest.left > 1)
      chunks.add(new chunk(largest.left, median - 1));	
    if(largest.right != largest.left)
      chunks.add(new chunk(median + 1, largest.right);
  }
  return median;
}
\end{lstlisting}

@@

\vspace {2 mm}
\begin{lstlisting}[basicstyle=\small,caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
--Initialize Variables
  Create vZ context 
  Create binary vector (x)
  Declare number of nodes, edges and $S_0$
  Declare hardware cost of each node as array (h) 
  Declare software cost of each node as array (s)
  Declare communication cost of each edge (c)
  Declare transposed incidence matrix graph G(E)
--Arithmetic Expressions
  SC = s(1-x)
  CMC = c*|EX|
  Fobj =  x[i] * h[i]
--Assert Constraints
  Add constraints (SF + CMC <= $S_0$)
  Add constraints to minimize Fobj
  Check Model
  Print Result
\end{lstlisting}
